Profiles of Wind Direction and Speed in Turbulent Ekman Flow

### 2021-09-09 write/manuscript.tex
finished section 3

\begin{figure}
  \begin{flushleft} 
    \textbf{a)}\hspace{0.47\textwidth} \textbf{b)}\\
    \includegraphics[width=\textwidth]{../plot/stresses.pdf}
    \textbf{c)}\hspace{0.47\textwidth} \textbf{d)}\\    
    \includegraphics[width=\textwidth]{../plot/eddy_viscosity.pdf}\\
  \end{flushleft} 
  \caption{
    \textbf{a-b)} Profiles of
    the turbulent stress $S_\mathrm{turb}^+$ (solid), 
    the viscous stress  $S_\mathrm{visc}^+$ (dotted), 
    and the total stress, $S^+=S_\mathrm{visc}^++S_\mathrm{turb}^+$ (dashed)
    as a function of inner height \textbf{(a)} and outer height \textbf{(b)}. 
    \textbf{c-d)} Normalized eddy viscosity $\nu_E$ (solid) plotted versus
    inner \textbf{(c)} and outer height \textbf{(d)}.
    Different colors are for different Reynolds numbers (cf. Tab.~\ref{tab:sim-setup}).
    Circles in \textbf{(a)} and \textbf{(b)} denote the height
    $z^-=0.15$, diamonds in \textbf{(c)} and \textbf{(d)} are for $z^+=50$
    as in Fig.~\ref{fig:profiles}.
    \label{fig:stresses}}  
\end{figure} 
The normalized viscous stress
\begin{subequations}
\begin{equation}
  S_\mathrm{visc}= \nu \sqrt\left(\frac{\p U}{\p z}\right)^2  + \left(\frac{\p V}{\p z}\right)^2}
\end{equation}
exhibits universal scaling when considered as $S_\mathrm{visc}^+(z^+)$ (Fig.~\ref{fig:stresses}c); this normalization is also appropriate in the outer layer where the viscous stress
is, however, small. 
%
Small deviations from the universal profile are observed for the smallest Reynolds number $\RE=500$; 
we attribute these to low-$\RE$ effects in the only transitionally turbulent flow ($\RE_\tau=479$). 
%
In contrast to the viscous stress, the total stress follows outer normalization, i.e.
$S^+(z^-)$ is universal.
%
This implies a mixed scaling for the turbulent stress, 
\begin{equation}
  S_\mathrm{turb} = \sqrt{\overline{uw}^2 + \overline{vw}^2}. 
\end{equation} 
Indeed, $S_\mathrm{turb}$ only follows inner normalization below $z^+\lesssim 20$
(where the turbulent contribution is negligible).
%
In the outer layer, where $S_\mathrm{visc}\rightarrow 0$, $S_\mathrm{turb}^+$
follows outer normalization for $z^-\gtrsim0.15$---with increasing accuracy for larger $\RE$ and larger distance from
the surface. 
%
In the overlap region, i.e. for $z^+>20$ and $z^-<0.15$, the mixed scaling for the
turbulent stress can be expressed as
\begin{equation}
  S_\mathrm{turb}^+(z^+,\RE_\tau) = S^+(z^-) - S_\mathrm{visc}^+(z^+), 
\end{equation}
where $z^-=z^+/\RE_\tau$. 
%
\par
%
The Eddy viscosity plays a crucial part when modelling profiles and the vertical
transport in turbulent flow. 
%
In analogy to the Fick-law for molecular diffusion, the eddy diffusivity is
the effective diffusivity that yields the turbulent transport $S_\mathrm{turb}$ based
on the strain rate.
%
For the symmetries in the flow (horizontal homoegeneity, and $W=0$), it is
%
\begin{equation}
  \nu_{E}= \frac{S_\mathrm{turb}}{\sqrt{\left(\frac{\p U}{\p z} \right)^2 + \left(\frac{\p V}{\p z}\right)^2}} = \nu \frac{S_\mathrm{turb}}{S_\mathrm{visc}}.  
\end{equation}
%
The inner normalization of $\nu_E$ s

\begin{eqnarray}
 \nu_E^+  \frac{Z_{\star}^{2}}{\delta+} &=& \frac{\nu_E^+}{\nu}
\end{eqnarray} 
\par
%
\todo{PARAGRAPH ON TURBULENCE STRUCTURE (2D SLICES, SPECTRA?) cf. Fig.~\ref{fig:slices}}

\begin{figure}
  \centerline{
    \includegraphics[trim=0 0 1152 0, clip, width=0.33\textwidth]{../plot/PLANES/tke_xz_10.pdf}
    \includegraphics[trim=1152 0 0 0, clip, width=0.33\textwidth]{../plot/PLANES/tke_xz_50.pdf}
    \includegraphics[trim=0 0 1152 0, clip, width=0.33\textwidth]{../plot/PLANES/tke_xz_400.pdf}}
  \centerline{
    \includegraphics[trim=1152 0 0 0, clip, width=\textwidth]{../plot/PLANES/tke_xy_1.pdf}}
  \caption{horizontal slices of turbulence kinetic energy in the
    Buffer layer (i=10),
    logarithmic Layer (i=100), and
    outer layer (i=400);
    coloring between percentiles 4 and 96 of the respective image. Lower panel:streamwise--vertical intersect through the domain 
    \label{fig:slices}}

>>>>

    \includegraphics[width=\textwidth]{../plot/stresses.pdf}
    \textbf{c)}\hspace{0.47\textwidth} \textbf{d)}\\    
    \includegraphics[width=\textwidth]{../plot/eddy_viscosity.pdf}\\
    \textbf{a-b)} Profiles of
    the turbulent stress $S_\mathrm{turb}^+$ (solid), 
    the viscous stress  $S_\mathrm{visc}^+$ (dotted), 
    and the total stress, $S^+=S_\mathrm{visc}^++S_\mathrm{turb}^+$ (dashed)
    as a function of inner height \textbf{(a)} and outer height \textbf{(b)}. 
    \textbf{c-d)} Normalized eddy viscosity $\nu_E$ (solid) plotted versus
    inner \textbf{(c)} and outer height \textbf{(d)}.
    Different colors are for different Reynolds numbers (cf. Tab.~\ref{tab:sim-setup}).
    Circles in \textbf{(a)} and \textbf{(b)} denote the height
    $z^-=0.15$, diamonds in \textbf{(c)} and \textbf{(d)} are for $z^+=50$
    as in Fig.~\ref{fig:profiles}.
    \label{fig:stresses}}  
The normalized viscous stress
  S_\mathrm{visc}= \nu \sqrt\left(\frac{\p U}{\p z}\right)^2  + \left(\frac{\p V}{\p z}\right)^2}
exhibits universal scaling when considered as $S_\mathrm{visc}^+(z^+)$ (Fig.~\ref{fig:stresses}c); this normalization is also appropriate in the outer layer where the viscous stress
is, however, small. 
Small deviations from the universal profile are observed for the smallest Reynolds number $\RE=500$; 
we attribute these to low-$\RE$ effects in the only transitionally turbulent flow ($\RE_\tau=479$). 
In contrast to the viscous stress, the total stress follows outer normalization, i.e.
$S^+(z^-)$ is universal.
This implies a mixed scaling for the turbulent stress, 
  S_\mathrm{turb} = \sqrt{\overline{uw}^2 + \overline{vw}^2}. 
Indeed, $S_\mathrm{turb}$ only follows inner normalization below $z^+\lesssim 20$
(where the turbulent contribution is negligible).
In the outer layer, where $S_\mathrm{visc}\rightarrow 0$, $S_\mathrm{turb}^+$
follows outer normalization for $z^-\gtrsim0.15$---with increasing accuracy for larger $\RE$ and larger distance from
the surface. 
In the overlap region, i.e. for $z^+>20$ and $z^-<0.15$, the mixed scaling for the
turbulent stress can be expressed as
  S_\mathrm{turb}^+(z^+,\RE_\tau) = S^+(z^-) - S_\mathrm{visc}^+(z^+), 
where $z^-=z^+/\RE_\tau$. 
The Eddy viscosity plays a crucial part when modelling profiles and the vertical
transport in turbulent flow. 
In analogy to the Fick-law for molecular diffusion, the eddy diffusivity is
the effective diffusivity that yields the turbulent transport $S_\mathrm{turb}$ based
on the strain rate.
For the symmetries in the flow (horizontal homogeneity, and $W=0$), it is
  \nu_{E}= \frac{S_\mathrm{turb}}{\sqrt{\left(\frac{\p U}{\p z} \right)^2 + \left(\frac{\p V}{\p z}\right)^2}} = \nu \frac{S_\mathrm{turb}}{S_\mathrm{visc}}.  
The inner normalization of $\nu_E$ is obtained by division through the molecular viscosity, and it is $\nu_E^+=\nu_E/\nu = S_\mathrm{turb}/S_\mathrm{visc}$. Under this normalization, the profiles of eddy viscosity collapse below $z^+\approx 20$ with a tendency towards better collapse
at higher $z^+$ (up to $z^+\approx 50$ for $\RE=1600$; Fig.~\ref{fig:stresses}b).
In the outer layer, the eddy viscosity is characterized by a distinct minimum at $z^-\approx 0.6-0.8$,
and we find that the following mixed normalization of $\nu_E$ by the geostrophic wind and friction velocity
collapses the value of $\nu_E$ at this minimum (cf. Fig.~\ref{fig:stresses}d): 
  \nu_E^-=\nu_E^+  \frac{Z_{\star}}{\delta^+} = \nu_E \frac{1}{\nu} \frac{G}{u_\star}\frac{\nu}{u_\star \delta}  = \nu _E \frac{Gf}{u_\star^3}. 
Substantial variation of the profiles is, however observed below and above this minimum for different $\RE$ which illustrates that
this normalization is probably not generally appropriate across the outer layer.
The organization of the flow is depicted in terms of the turbulence kinetic energy in Fig.~\ref{fig:slices}.
In vicinity of the wall, at $y^+\approx 10$, (Fig.~\ref{fig:slices}a), elongated streaks aligned with the
surface shear stress dominate.
Moving away from the wall, to $y^+\approx 150$ (well within the logarithmic region), the structures
are larger and more isotropic, but they are still largely aligned with the surface shear stress.
Finally in the upper part of the outer layer, around $y^+\approx 1000$, no clear visual signature of the
surface veering direction is found, and intense TKE structures (bright yellow)
are organized on a large spatial scale with with weaker eddies (greenish structures) and quiescent regions
in between.  
  \centerline{
    \includegraphics[trim=0 0 1152 0, clip, width=0.33\textwidth]{../plot/PLANES/tke_xz_10.pdf}
    \includegraphics[trim=1152 0 0 0, clip, width=0.33\textwidth]{../plot/PLANES/tke_xz_50.pdf}
    \includegraphics[trim=0 0 1152 0, clip, width=0.33\textwidth]{../plot/PLANES/tke_xz_400.pdf}}
  \centerline{
    \includegraphics[trim=1152 0 0 0, clip, width=\textwidth]{../plot/PLANES/tke_xy_1.pdf}}
  \caption{horizontal slices of turbulence kinetic energy in the
    Buffer layer (i=10),
    logarithmic Layer (i=100), and
    outer layer (i=400);
    coloring between percentiles 4 and 96 of the respective image. Lower panel:streamwise--vertical intersect through the domain 
    \label{fig:slices}}
